Reinforcement Learning Based Transmitter-Receiver Selection for Distributed MIMO Radars

### 2020-01-21 paper.tex
Modify references

A multi-armed bandit (MAB) framework, provides policies for selecting actions to balance the exploration and exploitation trade-off while maximizing the employed reward function \cite{Lattimore2019}.
In the literature, such a framework is effectively used for example in opportunistic spectrum access, in which the secondary user must choose frequency band in a way that interference to the primary user is not caused \cite{Zhao2008}.
Also, authors in \cite{Mukherjee2012} and \cite{Kuai2019} propose using a combinatorial MAB approach as a robust way for selecting the MIMO antenna subset for maximizing throughput in communication systems.
Extensions from combinatorial multi-armed bandits are used to address the problem with large combinatorial action space.

@@

Performance in target detection and target localization depend on the SINR level \cite{aittomaeki2011, Aittomaeki2018, Godrich2011, Sun2014}.
Therefore, a reward function for reinforcement learning is proposed that depends on the vector $\vsinrexp$ that consists of all the SINR values $\esinrexp$.
The following reward function is used for the employed MAB learning
\begin{equation}\label{eq:reward_func}
    r(\vasvrx, \vasvtx | \vsinrexp) = \frac{1}{N_S M_S}\sum_{n=1}^N \sum_{m=1}^M  \easvrx \easvtx \esinrexp,
\end{equation}
which is a mean of SINR values for the selected channels on a linear scale.
Furthermore, the reward maximization problem can be formulated as
\begin{equation}\label{eq:obj_func}
    \begin{array}{ll}
                &   \max_{\vasvrx, \vasvtx} r(\vasvrx, \vasvtx | \vsinrexp) \\[7pt]
    \text{s.t.} &   
                \left\{\begin{array}{l}
                    \sum_{n=1}^N \easvrx = N_S \\
                    \sum_{m=1}^M \easvtx = M_S.
                \end{array}\right.
    \end{array}
\end{equation}
It is possible to find an optimal solution for the equation (\ref{eq:obj_func}) if $\vsinrexp$ is known.
However, $\vsinrexp$ is not known since we can only obtain the measurements $\esp$. 
Furthermore, it might not be possible to probe all the channels at the same time.
Therefore, $\vsinrexp$ needs to be estimated from the received signal. 
By probing the different channels, an estimate $\vsinrb$ of the channel SINR values can be formed.
An approximate solution for the objective (\ref{eq:obj_func}) is found when the estimate $\vsinrb$ is used to condition the reward function (\ref{eq:reward_func}).
Different subsets must be explored sufficiently large number of times to reinforce the estimate $\vsinrb$ to identify the subset of TX-RX pairs yielding the highest SINR values.

@@

The MAB problem is a sequential decision-making problem in which an agent needs to decide on an action from several competing actions \cite{Sutton2018}.
The word arm originates from a slot machine that has a pull lever, and the pull lever is called an arm.
Pulling an arm of a slot machine gives a reward based on a certain probability distribution.
Moreover, the specific formulation considered in this paper is stochastic multi-armed bandits, in which each arm is associated with one state, thus with one reward distribution with constant or slowly changing parameters.
In the MAB problem, the agent needs to sequentially decide from many arms which arm to pull to maximize the cumulative reward.
The strategy of how the agent chooses the arms is called a policy.

@@

In practice, a policy is realized as an algorithm.
We briefly review five different MAB algorithms which are used in the simulations.
The selected algorithms are widely used to solve MAB problems.
These algorithms are
\begin{enumerate}
    \item $\epsilon$-greedy \cite{Sutton2018},
    \item Upper Confidence Bound (UCB1) \cite{Sutton2018, Garivier2008},
    \item Kullback Leibler Upper Confidence Bound (KL-UCB) \cite{Garivier2011},
    \item Thompson sampling \cite{Agrawal2011, Raj2017} and
    \item Recency-Based Exploration (RBE) \cite{Oksanen2015,Oksanen2017}.
\end{enumerate}
An analysis for stationary and non-stationary reward distributions can be found in the references.
Also, other algorithms and more extensive discussion on the multi-armed bandits can be found in \cite{Lattimore2019, Sutton2018, Burtini2015, Slivkins2019}.

@@

For the non-stationary case, the path-losses $\vpl$ and the angle-dependent scattering coefficients $\vrcs$ change in time.
In other words, the instantaneous SINR values $\vsinr$ are non-stationary and the channel SINR values $\vsinrexp$ are time-dependent.
The algorithms adapt to the non-stationary conditions by using the discounted action-value and discounted exploration parameters.
The discount factor is set to $\alpha = 0.998$.
Also, each element of $\vsinrb$ is divided by the maximum value before calculating the index.
This ensures that enough exploration is done at each time instant even if the scale of the rewards changes over time.
The value of $\epsilon$ for $\epsilon$-greedy algorithm is kept at 0.1.
The asymptotic optimality can not be achieved since the exploration term will never vanish completely.
However, the considered algorithms have differences in their exploration efficiencies, as can be observed from the different regrets in Fig.\ref{fig:non_stationary_regret}.

>>>>

A multi-armed bandit (MAB) framework provides policies for selecting actions to balance the exploration and exploitation trade-off while maximizing the employed reward function \cite{Lattimore2019}.
In the literature, such a framework is effectively used for example in opportunistic spectrum access, in which the secondary user must choose frequency band in a way that it does not cause interference to the primary user \cite{Zhao2008}.
Moreover, authors in \cite{Mukherjee2012} and \cite{Kuai2019} use a combinatorial MAB approach as a robust way for selecting the MIMO antenna subset for maximizing throughput in communication systems.
Extensions from combinatorial multi-armed bandits are used to address the problem with large combinatorial action space.

@@

Performance in target detection and target localization depend on the SINR level \cite{Aittomaeki2011, Godrich2011, Sun2014}.
Therefore, a reward function for reinforcement learning is proposed that depends on the vector $\vsinrexp$ that consists of all the SINR values $\esinrexp$.
The following reward function is used for the employed MAB learning
\begin{equation}\label{eq:reward_func}
    r(\vasvrx, \vasvtx | \vsinrexp) = \frac{1}{N_S M_S}\sum_{n=1}^N \sum_{m=1}^M  \easvrx \easvtx \esinrexp,
\end{equation}
which is a mean of SINR values for the selected channels on a linear scale.
Furthermore, the reward maximization problem can be formulated as
\begin{equation}\label{eq:obj_func}
    \begin{array}{ll}
                &   \max_{\vasvrx, \vasvtx} r(\vasvrx, \vasvtx | \vsinrexp) \\[7pt]
    \text{s.t.} &   
                \left\{\begin{array}{l}
                    \sum_{n=1}^N \easvrx = N_S \\
                    \sum_{m=1}^M \easvtx = M_S.
                \end{array}\right.
    \end{array}
\end{equation}
It is possible to find an optimal solution for the equation (\ref{eq:obj_func}) if $\vsinrexp$ is known.
However, $\vsinrexp$ is not known since we can only obtain the measurements $\esp$. 
Furthermore, it might not be possible to probe all the channels at the same time.
Therefore, $\vsinrexp$ needs to be estimated from the received signal. 
By probing the different channels, an estimate $\vsinrb$ of the channel SINR values can be formed.
An approximate solution for the objective (\ref{eq:obj_func}) is found when the estimate $\vsinrb$ is used to condition the reward function (\ref{eq:reward_func}).
Different subsets must be explored sufficiently large number of times to reinforce the estimate $\vsinrb$ to identify the subset of TX-RX pairs yielding the highest SINR values.

@@

The MAB problem is a sequential decision-making problem in which an agent needs to decide on an action from several competing actions \cite{Sutton2018}.
The word arm originates from a slot machine that has a pull lever, and the pull lever is called an arm.
Pulling an arm of a slot machine gives a reward based on a certain probability distribution.
Moreover, the specific formulation considered in this paper is stochastic multi-armed bandits, in which the arm rewards are generated from a single reward distribution.
In the MAB problem, the agent needs to sequentially decide from many arms which arm to pull to maximize the cumulative reward.
The strategy of how the agent chooses the arms is called a policy.

@@

In practice, a policy is realized as an algorithm.
We briefly review five different MAB algorithms which are used in the simulations.
The selected algorithms are widely used to solve MAB problems.
These algorithms are
\begin{enumerate}
    \item $\epsilon$-greedy \cite{Sutton2018},
    \item Upper Confidence Bound (UCB1) \cite{Sutton2018, Garivier2008},
    \item Kullback Leibler Upper Confidence Bound (KL-UCB) \cite{Garivier2011},
    \item Thompson sampling \cite{agrawal2012, Raj2017} and
    \item Recency-Based Exploration (RBE) \cite{Oksanen2015,Oksanen2017}.
\end{enumerate}
An analysis for stationary and non-stationary reward distributions can be found in the references.
Also, other algorithms and more extensive discussion on the multi-armed bandits can be found in \cite{Lattimore2019}.

@@

The algorithms adapt to the non-stationary conditions by using the discounted action-value and discounted exploration parameters.
The discount factor is set to $\alpha = 0.998$.
Also, each element of $\vsinrb$ is divided by the maximum value before calculating the index.
This ensures that enough exploration is done at each time instant even if the scale of the rewards changes over time.
The value of $\epsilon$ for $\epsilon$-greedy algorithm is kept at 0.1.
The asymptotic optimality can not be achieved since the exploration term will never vanish completely.
However, the considered algorithms have differences in their exploration efficiencies, as can be observed from the different regrets in Fig.\ref{fig:non_stationary_regret}.
